---
title: My dynamic report
output: html_fragment
---
## Running and temperature observations
This report summarises the running observations collected using my Google Form.  
Each response represents one outdoor run, and the report focuses on temperature, run duration, difficulty, and weather condition.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRZLlIccxMWtI2UC9pXfQM0_mamD1eaVuwhCzn6sYAKhBHRi29mZ2Zpbgq9Jlo1F9t4VZNYeR1WdXHo/pub?gid=1506109598&single=true&output=csv")

latest_data <- logged_data %>%
  rename(timestamp = 1,
         temp_c = 2,
         duration_min = 3,
         difficulty = 4,
         weather = 5)

num_runs <- nrow(latest_data)

min_temp <- min(latest_data$temp_c)
max_temp <- max(latest_data$temp_c)

mean_duration <- latest_data$duration_min %>%
  mean() %>%
  round(1)
```



```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  margin: 20px;
}

h2 {
  color: #1f4e79;
}

p {
  font-size: 15px;
}

img, svg {
  max-width: 100%;
}

```

A total of `r num_runs` runs were logged.

The lowest recorded temperature was `r min_temp` degrees Celsius, and the highest recorded temperature was `r max_temp` degrees Celsius.

The mean run duration was `r mean_duration` minutes.

The first bar chart shows how difficult the runs felt across the logged observations.

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = difficulty),
           fill = "#6a0dad") +
  labs(title = "How difficult did the runs feel?",
       subtitle = "Distribution of difficulty ratings across logged runs",
       x = "Difficulty",
       y = "Number of runs",
       caption = "Source: Running observation log")


```

```{r}


latest_data %>%
  ggplot() +
  geom_bar(aes(x = weather),
           fill = "#B2C248") +
  labs(title = "Weather conditions during runs",
       subtitle = "Count of logged runs by weather condition",
       x = "Weather condition",
       y = "Number of runs",
       caption = "Source: Running observation log")

```
```{r}


latest_data %>%
  ggplot(aes(x = temp_c, y = duration_min)) +
  geom_point(color = "#4DA6FF", size = 3) +
  labs(title = "Run duration vs outdoor temperature",
       subtitle = "Relationship between temperature and run duration",
       x = "Temperature (°C)",
       y = "Run duration (minutes)",
       caption = "Source: Running observation log")

```

```{r}


library(magick)

summary_text <- c(
  paste("Runs logged", num_runs),
  paste("Mean duration", mean_duration, "minutes"),
  paste("Minimum temperature", min(latest_data$temp_c), "degrees C"),
  paste("Maximum temperature", max(latest_data$temp_c), "degrees C")
)

frame1 <- image_blank(color = "white", width = 500, height = 500) %>%
  image_annotate(text = summary_text[1], size = 25, gravity = "center")

frame2 <- image_blank(color = "white", width = 500, height = 500) %>%
  image_annotate(text = summary_text[2], size = 25, gravity = "center")

frame3 <- image_blank(color = "white", width = 500, height = 500) %>%
  image_annotate(text = summary_text[3], size = 25, gravity = "center")

frame4 <- image_blank(color = "white", width = 500, height = 500) %>%
  image_annotate(text = summary_text[4], size = 25, gravity = "center")

frames <- c(frame1, frame2, frame3, frame4)

image_animate(frames, fps = 1)

```


